Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-30 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished the section unite buildings of the immediately previous step.

As shown in \eq\ref{eq:d_Et}, $\dtrm{E}$ increases along with time $t$.
We illustrated in \fig\ref{fig:ErosionBreak} that 
a larger $\dtrm{E}$ may result in the shrinking of a building.

$\dtrm[1]{G} + \dtrm[1]{D}$

@@

As we simplify buildings after growing, 
some parts of the buildings may shrink 
comparing to themselves at the immediately previous steps.
To avoid this shrink, we unite a building with itself at the immediately 
previous 
step so that the 
united building is always larger than both of the united parts.

>>>>

Both the erosion and line simplification may results in shrinking of a building.
\fig\ref{fig:Shrink_Erosion} and \fig\ref{fig:Shrink_Simplification} show such 
examples respectively.
To avoid these kinds of shrinking,
we unite a building with itself at the immediately previous step.
For example, if the grown polygons of 
\fig\ref{fig:Shrink_Erosion}~(c) and~(g) 
are from a sequence of $10$ steps, 
i.e., $t \in \{0.1, 0.2, \dots, 1\}$, 
then we compute the result of $t=0.8$ by uniting 
the grown polygon obtained independently at $t=0.8$ and 
the grown polygon at $t=0.7$. 
\fig\ref{fig:Shrink_Uniting}~(a) shows the result,
which is the union of the two grown polygons in 
\fig\ref{fig:Shrink_Erosion}~(c) and~(g).
Similarly, \fig\ref{fig:Shrink_Uniting}~(b) shows the union of the two grown 
polygons in 
\fig\ref{fig:Shrink_Simplification}~(c) and~(h).

@@
